Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-07 ba_resubmit/kundinger_resubmit2.tex
udpated draft

{\color{red}{The following paragraph is pretty unnecessary, I never use this notation}}
Denote the set of matches by $\bm{M} = \{(i,j): i \leq n_A, j \leq n_B, \Delta_{ij} = 1\}$, and the set of non-matches by 
$\bm{U} =  \{(i,j): i \leq n_A, j \leq n_B, \Delta_{ij} = 0\}.$ The record linkage task can be viewed as identifying  $\bm{M}$ and  $\bm{U}.$ We refer to record pairs that are estimated as matches as ``links'' and to record pairs that are estimated as non-matches as ``non-links.''

@@

{\color{red}{Beka suggested eliminating the following two paragraphs. Thoughts? I think the first one is good, the second seems unneccesary.}}

>>>>

%{\color{red}{The following paragraph is pretty unnecessary, I never use this notation}}
Denote the set of matches by $\bm{M} = \{(i,j): i \leq n_A, j \leq n_B, \Delta_{ij} = 1\}$, and the set of non-matches by 
$\bm{U} =  \{(i,j): i \leq n_A, j \leq n_B, \Delta_{ij} = 0\}.$ The record linkage task can be viewed as identifying  $\bm{M}$ and  $\bm{U}.$ We refer to record pairs that are estimated as matches as ``links'' and to record pairs that are estimated as non-matches as ``non-links.''

@@

%{\color{red}{Beka suggested eliminating the following two paragraphs. Thoughts? I think the first one is good, the second seems unneccesary.}}
